\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{green}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\setlength{\hintscolumnwidth}{3cm}

\name{Vitalii}{Repeev}
\title{QA Engineer}
\phone[mobile]{+79172831892}
\email{vitallalom@gmail.com}
\social[linkedin]{https://www.linkedin.com/in/purepx/}
\social[github]{https://github.com/PurePX}
\social[telegram]{@vitallalom}

\begin{document}
\makecvtitle
\vspace{-5mm}
\section{Summary}
Experienced QA Engineer proficient both in manual and automated testing, using various testing frameworks. Skilled in Ruby, C\# and Rust, with a proven track record of implementing and maintaining automated test systems. Strong collaboration abilities and unique point of view ensured projects glow up in various software development spheres like Gamedev, Healthcare and POS systems.

\section{Experience}

\cventry
{Jun 2023 -- Present}
{QA Engineer}
{SalonUltimate}
{}{}
{Responsible for quality assurance for the industry's most advanced cloud software and point of sale solution. Key achievements include:
\begin{itemize}
\item Implemented a complex automated testing framework into both development and QA processes, resulting in improved regression routines coverage and a reduction in defects.
\item Introduced a new test documentation management approach for the entire QA department, significantly enhancing test repository maintainability and reducing the time required for creating test documentation, ultimately ensuring optimal QA performance.
\item Solely conducted quality assurance for the cloud-based high-load core system serving top-tier customers, facilitating their rapid growth, satisfaction, and contributing to increased company profits.
\item Actively engaged in strategic decision discussions with stakeholders for both internal and external projects.
\end{itemize}}

\cventry
{Feb 2022 -- Jun 2023}
{QA Engineer}
{Mercury Development}
{}{}
{Performed quality assurance for one of the largest U.S. medical and healthcare insurance companies' internal services and websites. Key achievements include:
\begin{itemize}
\item Successfully automated QA routines and established a test automation framework from scratch.
\item Consistently delivered high-quality features across multiple projects simultaneously.
\item Actively engaged in multiple projects concurrently, leading to the creation of a valuable knowledge base and providing onboarding and mentorship to other QA Engineers.
\item Earned a rapid promotion in recognition of exceptional performance and significant contributions to the team.
\end{itemize}}

\cventry{Dec 2019 -- Aug 2021}{QA Engineer}{Vault44}{}{}{
\begin{itemize}
\item Tested and troubleshot custom and enterprise software, ensuring functionality and performance.
\item Analyzed logs and metrics, improving system reliability.
\item Addressed client feedback, enhancing user satisfaction.
\item Managed automatic software deployment and hardware maintenance.
\item Increased system uptime from \textbf{70\% to 98.7\%,} resulting in a \textbf{30\%} profit boost.
\item Designed two branch computer systems from scratch, showcasing technical expertise and adaptability.
\end{itemize}}

\section{Skills}

\subsection{Testing}
\cvitem{}{Manual, Automated, Web, Desktop, Mobile, Automated Testing Frameworks, Test Methodologies}

\subsection{Tools and Technologies}
\cvitem{}{Jira, Xray, C\#, Rust, Ruby, Selenium, Specflow, Postman, Fiddler, JMeter, Android Studio, SQL, Jenkins}

\subsection{Project Management and Methodologies}
\cvitem{}{Agile Methodologies, Software Development Life Cycle (SDLC), Software Quality Assurance, Cybersecurity, Incident Response, Risk Management, Team Leading}

\section{Languages}
\cvitem{}{Russian: Native \hspace{1cm} English: Advanced (Scientific and Business) \hspace{1cm} French: Elementary}



\section{Education}
\cventry{2017 -- 2021}{Bachelor of Science}{Kazan National Research Technological University}{Kazan}
{}{Major: Biotechnology\newline{}
Thesis: "Phytotoxicity analysis of agrominerals used as mineral fertilizers"
\begin{itemize}
\item Participated in the Biotech Club, hosting events like seminars, workshops, and excursions related to biotechnology;
\item Member of the university's programming club, practicing programming skills and enhancing the learning experience of fellow students.
\end{itemize}
Courses completed in statistics, data analysis, and scientific writing, which have proven invaluable in my QA Engineer career. Developed leadership, teamwork, and communication skills through active involvement in extracurricular activities.}

\cventry{}{Additional Education}{Higher school of foreign languages "Lingva"}{Kazan}{\textit{Scientific and Business English.}}
{Improved language skills and ability to effectively communicate with colleagues and clients from diverse cultural and linguistic backgrounds.}

\end{document}